### 2025-07-16 paper/quarto_aaai/paper.tex
minor adjustments ot table 1 caption

\caption{\label{tbl-main}Key performance metrics and bootstrapped
standard errors (omitted if essentially zero) for all datasets.
\textbf{Plausibility} (columns 1-2): percentage reduction in
implausibility for \(\text{IP}\) and \(\text{IP}^*\), respectively;
\textbf{Actionability} (column 3): percentage reduction in costs with
protected features. \textbf{Accuracy} (columns 4-7): test accuracies and
robust accuracies (\(\text{Acc}^*\)) for CT and the baseline (BL).
Counterfactual outcomes in columns 1-3 are aggregated across bootstrap
samples and varying degrees of the energy penalty
\(\lambda_{\text{egy}}\) used for \emph{ECCo} at test time. Asterisks
(\(^*\)) in columns 1-3 indicate that difference is statistically
significant at 1\%-level. Standard errors for accuracy are bootstrapped
from the test set.}

>>>>

\caption{\label{tbl-main}Key performance metrics and bootstrapped
standard errors (omitted if essentially zero) for all datasets.
\textbf{Plausibility} (columns 1-2): percentage reduction in
implausibility for \(\text{IP}\) and \(\text{IP}^*\), respectively;
\textbf{Actionability} (column 3): percentage reduction in costs with
protected features. \textbf{Accuracy} (columns 4-7): test accuracies and
robust accuracies (\(\text{Acc}^*\)) for CT and the baseline (BL).
Counterfactual outcomes (col.~1-3) are aggregated across bootstrap
samples and varying degrees of the energy penalty
\(\lambda_{\text{egy}}\) used for \emph{ECCo} at test time. Asterisks
(\(^*\)) in columns 1-3 indicate that bootstrapped 99\%-confidence
interval of differences in mean outcomes does \emph{not} include zero.
Standard errors for accuracy (col.~4-7) are bootstrapped from the test
set.}

### 2025-07-16 paper/sections/experiments.qmd
asterisks added and rerendered
minor adjustments ot table 1 caption

Key performance metrics and bootstrapped *two* standard errors for all datasets. **Plausibility** (columns 1-2): percentage reduction in implausibility for $\text{IP}$ and $\text{IP}^*$, respectively; **Actionability** (column 3): percentage reduction in costs with protected features. **Accuracy** (columns 4-7): test accuracies and robust accuracies ($\text{Acc}^*$) for CT and the baseline (BL). Counterfactual outcomes in columns 1-3 are aggregated across bootstrap samples and varying degrees of the energy penalty $\lambda_{\text{egy}}$ used for *ECCo* at test time. Standard errors for accuracy are bootstrapped from the test set.
:::

>>>>

Key performance metrics and bootstrapped standard errors (omitted if essentially zero) for all datasets. **Plausibility** (columns 1-2): percentage reduction in implausibility for $\text{IP}$ and $\text{IP}^*$, respectively; **Actionability** (column 3): percentage reduction in costs with protected features. **Accuracy** (columns 4-7): test accuracies and robust accuracies ($\text{Acc}^*$) for CT and the baseline (BL). Counterfactual outcomes (col. 1-3) are aggregated across bootstrap samples and varying degrees of the energy penalty $\lambda_{\text{egy}}$ used for *ECCo* at test time. Asterisks ($^*$) in columns 1-3 indicate that bootstrapped 99%-confidence interval of differences in mean outcomes does *not* include zero. Standard errors for accuracy (col. 4-7) are bootstrapped from the test set.
:::
